A Study of Immersion Factors Using an Augmented Reality Simulation

### 2009-06-20 Paper/paper.tex

\title{Title Goes Here}

@@

\section{Experimental Design}

@@

Participants are presented a view of the scene through a head-mounted display helmet with orientation tracking.  The tracking overlays are  augmented on top of the image to form the simulated augmented reality view.

@@

@@

\section{Results}

\section{Analysis}

\section{Conclusions}

>>>>

\title{A Study of Immersion Factors Using an Augmented Reality Simulation}

@@

\section{AR Simulator Validation}

Cha's text goes here

\subsection{Experimental Design}

\subsection{Results}

\subsection{Analysis}

\section{Tracking Study}

@@

@@

\subsection{Experimental Design}
Participants are presented a view of the scene through a head-mounted display helmet with orientation tracking.  The tracking overlays are  augmented on top of the image to form the simulated augmented reality view.

@@

\subsection{Results}

\subsection{Analysis}

\section{Conclusions and Future Work}
